Constant-round Blind Classical Verification of Quantum Sampling

### 2020-09-11 introduction.tex
Make phrasing more concise
Make editorial changes

\Ethan{This paragraph is new and has to be checked}
Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
it is still unclear how to construct a CVQC protocol for $\SampBQP$.
A protocol for classical sampling problems is usually obtained from that of decision problems,
by fixing a seed for pseudorandomness then computing the output bit-by-bit.
This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements,
where the outcome is generally different from one execution to the next.
Furthermore, it is unclear how to even amplify the soundness of a sampling protocol by means of repetitions,
especially considering the outputs from different executions might be correlated to begin with.

>>>>

\Ethan{This paragraph is new and has to be checked}
Even with the CVQC protocol for $\BQP$ from \cite{FOCS:Mahadev18a}, however,
it is still unclear how to construct a CVQC protocol for $\SampBQP$.
A protocol for classical sampling problems is usually obtained from that of decision problems,
by fixing a seed for pseudorandomness then computing the output bit-by-bit.
This does not work for $\SampBQP$ since randomness from quantum computations arises from measurements.
Additional challenge comes from modeling and achieving soundness for such a sampling protocol,
since it is unclear how to use the usual trick of running many copies of the protocol then applying the Chernoff bound.

### 2020-09-11 qpip0.tex
Make editorial changes

	where we used triangle inequality on the second line, \Cref{thm:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
	Let $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$ and by triangle inequality we have $\tr\abs{z-z_{ideal}}=O(\varepsilon)$.
	Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its accept probability too.
\end{proof}

>>>>

	where we used triangle inequality on the second line, \Cref{thm:zi-zgoodi} on the third line, Equation~\ref{eq:bad-term-sum} and Cauchy's inequality on the fourth line.
	Let $m=O(1/\eps^2), T=O(1/\eps^2),\gamma_0=\eps^8$ and by triangle inequality we have $\tr\abs{z-z_{ideal}}=O(\varepsilon)$.
	Since $z$ is close to some ideal output distribution $z_{ideal}$, it must be close to the ideal output distribution with its own accept probability too.
\end{proof}
